# Introduction {-}

This code presented in this workbook is meant to accompany the study,
and give the reader the possibility to reproduce (or built) upon the analyses
presented in the manuscript.

The conceptualization, majority of the code and organization was 
created by [Timo Röder](https://0000-0001-6841-4056) with some later changes and updates 
by [Patrick Munk](https://orcid.org/0000-0001-8813-4019).

# Data Sources {-}

* European Nucleotide Archive:
  + Raw FASTQ data
* Zenodo:
  + CatMapstat files
  + Reference GenomicsDB metadata
  + ResFinder Metadata
* Supplementary Material:
  + Count matrices
  + Sample Metadata
  + ResFinder Metadata
  + Summary statistics
  + Microbiome statistical results
* Analysis code:
  + Github

# R Packages {-}
You will need to load the following packages at some point during the analysis,
so best go ahead and install them.
```{r load-all-pkgs, message=FALSE}
library(ALDEx2)
library(tidyverse)
library(mapstatHelpers)
library(pheatmap)
library(cowplot)
library(ggrepel)
library(viridisLite)

include_samples <- livestock_sample_metadata %>% 
  group_by(species, country, farm_id) %>% 
  mutate(fragment_rank = min_rank(desc(total_fragments))) %>% 
  filter(fragment_rank == 1) %>% 
  .$sample_id
```
# Plot colors
Let us define some colors that we can use throughout plots
```{r plot-colors}
plot_colors = list(explicit_country = c(BE="#E41A1C", BG="#377EB8", DE="#4DAF4A", 
                                        DK="#984EA3",ES="#FF7F00", FR="#FFFF33", 
                                        IT="#A65628", NL="#F781BF", PL="#999999"),
                   country = c(A="#E41A1C", B="#4DAF4A", C="#984EA3", 
                               D="#A65628", E="#FFFF33", F="#F781BF", 
                               G="#999999", H="#FF7F00", I="#377EB8"),
                   species = c(Fish="#386cb0", Pig = "#beaed4", Broiler="#fdc086", 
                               Turkey="#ffff99", "Veal Calf"="#7fc97f"),
                   nofish = c(Pig="#beaed4", Broiler="#fdc086", Turkey="#ffff99", "Veal Calf"="#7fc97f"))
```

# Loading metadata
The metadata on the investigated samples is available in flat tab-separated files.
The same is the case for the ResFinder resistance genes. So let us load them.

```{r load-metadata, , message=FALSE}
# Load sample metadata
livestock_sample_metadata = read_tsv("study_metadata/livestock_sample_metadata.txt")

# Load ResFinder metadata
resfinder_metadata = read_tsv("study_metadata/resfinder_metadata.txt")
```


```{r print-sessionInf}
# devtools::session_info()
```

